The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-09-13 paper.tex
Revise section on Quantum Simulation

\sihui{
\subsection{Quantum simulations}
Quantum simulations is about simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this. The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes. Progress using this approach has already been discussed in Section \ref{sec:LOQC}. `The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems. We focus on discussing analog quantum simulation in this section.

 Quantum interferometers have been proposed and in some cases implemented as quantum simulators. In quantum chemistry, the energy spectrum of the hydrogen molecule has been calculated using a quantum simulator comprising of a pair of entangled photons in a polarization-dependent interferometer \cite{bib:Lanyon10}. With two entangled photon pairs, valence-bond states have been simulated and a fiber-based tunable directional coupler gives analogue control over superpositions of different valence-bond states \cite{bib:Ma2011}. The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}. Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, and behavior transitions in tight-binding Hamiltonians \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13}.
  }

>>>>

\sihui{
\subsection{Quantum simulations}
Quantum simulations is about simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this. The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes. Progress using this approach has already been discussed in Section \ref{sec:LOQC}. The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems. We focus on discussing analog quantum simulation in this section. Further discussions can be found in reviews written on quantum simulations \cite{bib:Buluta108, bib:Georgescu14}, including one specifically for optical quantum simulations \cite{bib:Aspuru-Guzik12}.

 Quantum interferometers have been proposed and in some cases implemented as quantum simulators. In quantum chemistry, the energy spectrum of the hydrogen molecule has been calculated using a quantum simulator comprising of a pair of entangled photons in a polarization-dependent interferometer \cite{bib:Lanyon10}. With two entangled photon pairs, valence-bond states have been simulated and a fiber-based tunable directional coupler gives analogue control over superpositions of different valence-bond states \cite{bib:Ma2011}. The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}. Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, transitions between fermionic and bosonic behavior \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13,bib:Keil16}, fractional statistics of anyons \cite{bib:Han07,bib:Pachos09, bib:Chao-Yang09}, and excitation transfer in biological systems \cite{bib:Caruso11,bib:Viciani16}.
  }
